\subsection{Collaboration}\todo{work on this part}
major factor in office design: supporting different styles of work. collaborative work needs places where ``the atmosphere is
conducive to innovation'', i.e. not as boring as a normal meeting room. however, there must also be place to receive phone calls and to work concentrated on a project etc., i.e. silent working areas are needed.\cite{tieto}

If these areas are provided, the employees must be able to freely move between these areas. therefore the office must provide an``instant, real-time picture of what's going on'' so that the people see where space is available. It is also crucial that the office provides a way to see where colleagues are working as they are able to freely move between different areas. \cite{tieto}

Example of working together: spontaneous meetings, just see who'S around, where's room and go. \cite{tieto}

\cite{roomzilla3} mentions that an exciting workplaces may lead to more creative employees and more comraderie between employees. Typically it is assumed that such a playful environment is detrimental to the productiviy of employees. However, according to \cite{metroffice}, such environments can actually lead to a more successful business because the employees are more motivated and creative.

In \cite{hbcommunications} it is stated that a streamlined communication and improved connectivity leads to better and faster collaboration. The authors describe how this can make finding experts in the organization easier.

Speaking of communication, having a smart workplace can have a big impact on overall corporate culture within an organization. People expect their workplaces to have technology that’s at least as good as what they have at home—preferably better—and this is especially true for those digital natives, the Millennials. Studies show that happy employees are productive employees and productive employees lead to prosperous businesses. Equally as important is the ability of companies to not only attract, but also to retain top talent. When you create a workplace that is a pleasure to be in and work in and provide state-of-the-art technology, it goes a long way toward making employees want to stay around. easier life for office management: lights turn on and off automatically, temperature regulation via thermostats \(\rightarrow\) safe energy. more fun workplace with: coffee pots, fitness equipment, or wearables that track fitness and reward employees for
reaching certain fitness goals\cite{hbcommunications}

