\section{Introduction}
There's lot of activity in the office. Tracking the activity via IoT can lead into new insights about these behaviours. Knowledge can be used to improve: productivity, engagement, safety \cite[iotagenda].

well-organized, efficient, enjoyable workplace and serve the employees who inhabit that space on a daily basis.\cite[hbcommunications]

impacts everything from energy efficiency and convenience (like lights that automatically go on when a room is occupied), to enhanced
collaboration spaces, to improved employee communication. \cite[hbcommunications]

\paragraph{related research}
living lab is a real open space working area which includes an experimentation room. This lab was created because studies in real working environments are hard to do: the situation cannot be controlled and the study must impact the working people as less as possible. To conduct research, controlled study bedingungen\todo{translate} are needed. However, results achieved in especially created experiment rooms are hard to transfer to real world situations. \cite[living-lab]

The living lab combines these conflicting areas of interest. The lab itself is an open space with with flexible working stations. The lab also has a clean desk policy, i.e. the people working there do not have a fixed desk but choose their working place each day according to availability.\cite[living-lab]

The living lab has researched different types of technologies. Examples include electrochromatic glass which can be turned dark on demand to prevent sunlight from shining trough or personlaized air flow optimization for workers. The living lab tests these technologies in simulations and real life situations. Another area of research is light and acoustic optimization. Good lighting and acoustics cannot be measured directly as most people only notice bad lighting or bad acoustics. \cite[living-lab]

Modern LEDs provide great ways to improve the worker's productivity by adapting intensity and the color specturm. It has been shown in recent research that the color spectrum directly influences the activity and the biorhythmus of people. In acoustics, a good level of ``noise'' has to be found. Most open area offices are too quiet and as such talks between colleaguas and phone calls distract other people. However, too loud environments are also detrimental to work. Therefore the right balance as to be fouind to optimize the worker's productivity.   
\cite[living-lab]

