\subsection{Well-Being}

E.g.: Customize lighting and heating \(\rightarrow\) more comfortable working enviroment\cite{iotagenda}

Speaking of communication, having a smart workplace can have a big impact on overall corporate culture within an organization. People expect their workplaces to have technology that’s at least as good as what they have at home—preferably better—and this is especially true for those digital natives, the Millennials. Studies show that happy employees are productive employees and productive employees lead to prosperous businesses. Equally as important is the ability of companies to not only attract, but also to retain top talent. When you create a workplace that is a pleasure to be in and work in and provide state-of-the-art technology, it goes a long way toward making employees want to stay around. easier life for office management: lights turn on and off automatically, temperature regulation via thermostats \(\rightarrow\) safe energy. more fun workplace with: coffee pots, fitness equipment, or wearables that track fitness and reward employees for
reaching certain fitness goals\cite{hbcommunications}

4 key drivers or enablers of change within the workplace strategy area: 1. Cost/price pressure; 2. Sustainability \& Corporate Responsibility; 3. Technology; and 4. the War for talent \& Productivity area\cite{hub13}

% 1. rents are very expensive, especially in nordic countries. utilizization of office space rarely exceeds 50\%.
% \cite{hub13}

% 2. sustainability becomes more and more important. sustainability becomes more of a business opportunity\cite{hub13}

% 3. technology becomes more and more sophisticated and can enable change.\cite{hub13}

4. talented workers are scarce and productivity needs to be optimized. different issues here: unemployment is high but both public and private employers struggle to find people\todo{drop?}, variation at workplace (multi-generation workplace, multi-cultural environment), disengaged workers doing subpar work, workplaces hindering productivity, strong relationship between comfort and self-reported productivity (diff of 25\% between comfortable and uncomfortable staff)\cite{hub13}

people are very expensive, improving their wellbeing can highly impact the financial state of the company. \cite{hub13}
